\chapter{Graph}

\section{Theorems}
% 1. in bipartite graph, |max flow| = |max matching| = |min vertex cover|, min vertex cover = v - max independent set (konig's theorem)
% 2. In any graph without isolated vertices, |min edge cover| + |max matching|= |v|
% 3. combining 1, 2, in bipartite with no isolated graph, |minimum edge cover| = |maximum independent set|

% 이거랑 network의 edge가 모두 unit capacity거나, 더 general 하게는 src와 sink를 제외한 모든 vertex가 (outgoing edge가 1개고 이것이 unit capacity) or (incoming edge가 1개고 이것이 unit capacity)일 때 dinic이 O(E * min(V^2/3, E^1/2)) 으로 평소보다 빠르다
\textbf{Konig's Theorem} In any bipartite graph, $\abs{\text{max flow}} = \abs{\text{max matching}} = \abs{\text{min vertex cover}}$. Also, $V - \abs{\text{max indep set}}$. 

In any graph without isolated vertices, $\abs{\text{min edge cover}} + \abs{\text{max matching}} = V$

$\Rightarrow$ For bipartite graph of no isolated edge,  $\abs{\text{min edge cover}} = \abs{\text{max indep set}}$

\textbf{Flow complexity} When all edges are unit capacities (or more generally for all intermediate vertices, there are one in/out edge of unit capacity), Dinic's algorithm runs in $O(E \min(V^{2/3}, E^{1/2}))$
\section{Trees}
	\kactlimport{LCA.h} % Todo
	\kactlimport{HLD.h}
	\kactlimport{LinkCutTree.h}
	\kactlimport{DirectedMST.h}
    \kactlimport{CentroidDecomp.h}

\section{Strongly Connected Components}
	\kactlimport{SCC.h}
	\kactlimport{BiconnectedComponents.h}
	\kactlimport{2sat.h}

\section{Euler Tour}
	\kactlimport{EulerWalk.h}

\section{Network flow}
	\kactlimport{Dinic.h}
	\kactlimport{MinCostMaxFlow.h}

	\paragraph{L-R MaxFlow} (1) MCMF solution. For edge (a$\to$b) with bound $[l, r]$, make two edges as $(l, -1), (r-l ,0)$. MCMF forces flow to remaining $-1$ edges. COST : is there possible lr-flow. FLOW : actual lr-flow. (2) Dinic solution. Make new SRC and SNK. Make (SNK, SRC, INF) edge. For edge (a$\to$b) with bound $[l, r]$, make $(a \to \text{NEWSNK}, l)$, $(\text{NEWSRC} \to b, l)$, $(a\to b, r-l)$. Is sum of maxflow $\text{NEWSRC} \to \text{NEWSNK}$ equal to sum of $l$? To find actual flow, run dinic again with original SRC-SNK (without resetting).
	\kactlimport{EdmondsKarp.h}
	\kactlimport{MinCut.h}
	\kactlimport{GlobalMinCut.h}
	% \kactlimport{GomoryHu.h}

\section{Matching}
	\kactlimport{hopcroftKarp.h}
	\kactlimport{Hungarian.h}
	\kactlimport{DFSMatching.h}
	\kactlimport{MinimumVertexCover.h}
	\kactlimport{WeightedMatching.h}
	\kactlimport{GeneralMatching.h}

\section{Heuristics}
	\kactlimport{MaximalCliques.h}
	\kactlimport{MaximumClique.h}
	\kactlimport{MaximumIndependentSet.h}
